### 2019-01-08 writing/thesis/chapters/methods.tex
Some proof changes.

% Stuff for numerics
\newcommand{\domain}{\Omega}
\newcommand{\broken}{\domain}
\newcommand{\cell}[1][]{C_{#1}}
\newcommand{\boundary}{\partial \domain}
\NewDocumentCommand{\sbasis}{ O{} O{} }{\phi^{#1}_{#2}}
\NewDocumentCommand{\stbasis}{ O{} O{} }{ \Theta^{#1}_{#2}}
\NewDocumentCommand{\sbasisRef}{ O{} O{} }{\hat{\phi}^{#1}_{#2}} %{\hat{\sbasis[#1][#2]}}
\NewDocumentCommand{\stbasisRef}{ O{} O{} }{\hat{\Theta}^{#1}_{#2}} %{\hat{\stbasis[#1][#2]}}
%\newcommand{\stestfunction}[1]{\sbasis[#1]}
\NewDocumentCommand{\stestfunction}{ O{} O{} }{\sbasis[#1][#2]}
\NewDocumentCommand{\sttestfunction}{ O{} O{} }{\stbasis[#1][#2]}
\newcommand{\normal}{\bm{n}}
\newcommand{\dsol}[1][h]{\bm{u}_{#1}}
\NewDocumentCommand{\stpredictor}{ O{} O{} }{\overline{\bm{q}}^{#1}_{#2}}
\NewDocumentCommand{\spredictor}{ O{} O{} }{\bm{q}^{#1}_{#2}}

@@

The Jacobian determinant of $\mapping$ is simply the volume $V$ of the cell
\begin{equation}
  \label{eq:determinant-mapping}
  \volume = \operatorname{det}(\operatorname{Jacobian}\mapping) = \Delta x \, \Delta y \,\Delta z,
\end{equation}
the Jacobian determinant of $\timeMapping$ is $\Delta t$.
This is useful for evaluating derivatives by the chain rule and, similarly, integrals by substitution.
For example, we can evaluate a volume integral by
\begin{equation}
  \label{eq:integration-by-substitution}
  \intdcell{
f(\bm{x})
  }
  =
\volume \intdrefcell{
    \hat{f}(\hat{\bm{x}})
  }
\end{equation}
\sidetitle{Basis Functions}
\newcommand{\lagrange}[1][i]{\varphi_{#1}}
\newcommand{\lagrangeRef}[1][i]{\hat{\varphi}_{#1}}
The next step is the definition of basis functions for the reference cell.
We use Langrange polynomials that are defined in the one-dimensional case by
\begin{equation}
  \label{eq:lagrange-basis}
  \lagrangeRef(x) = \prod_{i \neq j}^N \frac{x - x_j}{x_i - x_j}.
\end{equation}
We can then represent functions as a sum over the support points $x_j$
\begin{equation}
  \label{eq:langrange-expansion-1d}
  f(x) = \sum_{i = 0}^N f(x_i) \lagrangeRef[i](x) = f(x_i) \lagrangeRef[i](x),
\end{equation}
where we used the Einstein summation convention where summation over repeated indices is implied\todo{Remove this sentence, or sentence before introducing einstein summation!}.
The support points $x_i$ are chosen such that they coincide with the nodes of the Gauss-Legendre quadrature which we can use to evaluate integrals
\begin{equation}
  \label{eq:quadrature-1d}
  \int_0^1 f(x) \dd{x} = \sum_n^N \quadWeight[n] f(x_n),
\end{equation}
where $x_n$ is a quadrature point with weight $\quadWeight[n]$.

The basis functions are similarly defined in $d$-dimensions by considering nodes that are the tensor-products of $d$ one-dimensional Gauss-Legendre quadrature.
To simplify notation, we order the polynomials by a linearised index, a $d$-dimensional function is then approximated by
\begin{equation}
  \label{eq:lagrange-expansion}
  f(\bm{x}) = \sum_{i = 0}^{(N+1)^\dimensions - 1} f(\bm{x}_i) \lagrangeRef[i](\bm{x}) = f(\bm{x}_i) \lagrangeRef[i](\bm{x}).
\end{equation}
Similarly to the one-dimensional case, we can evaluate integrals by
\begin{align}
  \label{eq:quadrature}
  \underbrace{\int_0^1 \cdots \int_0^1}_{\dimensions \text{ times}} f(\bm{x}) \dd{\bm{x}} &= \sum_n^{(N+1)^D - 1} \quadWeight[n] f(\bm{x}_n) \\
  \intertext{with}
  \quadWeight[n] &= \prod_{i}^{d} \quadWeight[i].
\end{align}
\todo{Fix notation, especially multi-dimensional integral.}
\todo{Check number of total polynomials.}
% TODO: Quadrature

Two important properties of this family of polynomials are
  \begin{alignat}{10}
    \label{eq:basis-interpolating}
&& \text{Interpolating:} \qquad && \lagrangeRef[i] (\quadNode[i]) &= \delta_{ij}\\
\label{eq:basis-orthogonality}
&& \text{Orthogonality:} \qquad &&
\underbrace{\int_0^1 \cdots \int_0^1}_{d \,\text{times}}
\lagrangeRef[i] \left( \hat{\bm{x}} \right)
\lagrangeRef[j] \left( \hat{\bm{x}} \right) \dd{\hat{\bm{x}}}
&= \quadWeight[i] \delta_{ij}
    \end{alignat}

We will later need basis functions over a space-cell
$v = 0, \ldots, \NVar, n = 0, \ldots, (N+1)^{\dimensions} - 1, l=0,\ldots,N$
\begin{align}\label{eq:space-basis}
  \begin{split}
  \sbasisRef[][n] (\hat{\bm{x}}) &= \lagrange[n] (x)\\
  \sbasis[][n] (\bm{x}) &= \sbasisRef[][n] \left( \mapping(\bm{x}) \right)
  \end{split}
\end{align}
where $\sbasisRef$ denotes the basis function on the reference cell.
Similarly, we define a basis for a space-time element defined over $(0, 1)^D \times (t^n, t^{n+1})$
\begin{align}\label{eq:space-time-basis}
  \begin{split}
  \stbasisRef[][l,n](\hat{\bm{x}}, \hat{t}) &= \lagrange[l](t) \sbasis[][n] (x) = \lagrange[l](t) \lagrange[n](x)\\
  \stbasis[][l,n] (\bm{x}, t) &= \stbasisRef \left( \mapping(\bm{x}), \timeMapping(t) \right)
  \end{split}
\end{align}
Outside of elements, we define the basis functions to be equal to 0.
\todo{Bold x, bold t?}
\todo{Variables in basis, tensor product?}

@@

We integrate the first term by parts in time and the flux divergence in space.
Here we do not use the Riemann solver for the flux boundary term but rather use the discrete solution at time $t$\todo{Insert in equation!}.
This corresponds to upwinding in time~\cite{dumbser2008unified}.
Note that this neglects the interaction with neighbouring cells.
We account for this in the corrector step.
\begin{align}\label{eq:space-time-predictor}
\begin{split}
\intdcell{
  \sttestfunction[\cell][k] (\bm{x}, t^{n+1}) \stpredictor(\bm{x}, t^{n+1})
}
&-
\intdt{\intdcell{
    \pdv{}{t} \sttestfunction[\cell][k] (\bm{x}, t) \stpredictor(\bm{x}, t)
}}
= \\
\intdcell{
  \sttestfunction[\cell][k] (\bm{x},t^n) \stpredictor(\bm{x}, t^n)
}
&+
\intdt{\intdcell{
    \sttestfunction[\cell][k] (\bm{x},t) \divergence{\flux(\stpredictor, \gradient{\stpredictor})}
}}
+
\intdt{\intdcell{
    \sttestfunction[\cell][k] (\bm{x}, t) \source(\stpredictor)
}}
\end{split}
\end{align}
\NewDocumentCommand{\stpredictorCoeff}{ O{} O{} }{\underline{\overline{q}}^{#1}_{#2}}
\NewDocumentCommand{\stflux}{ O{} O{} }{\overline{F}^{#1}_{#2}}
\NewDocumentCommand{\stfluxCoeff}{ O{} O{} }{\underline{\overline{F}}^{#1}_{#2}}
\NewDocumentCommand{\stsource}{ O{} O{} }{\overline{S}^{#1}_{#2}}
\NewDocumentCommand{\stsourceCoeff}{ O{} O{} }{\underline{\overline{S}}^{#1}_{#2}}
\NewDocumentCommand{\spred}{ O{} O{} }{u^{#1}_{#2}}
\NewDocumentCommand{\ssolCoeff}{ O{} O{} }{\underline{u}^{#1}_{#2}}
\NewDocumentCommand{\sflux}{ O{} O{} }{F^{#1}_{#2}}
\NewDocumentCommand{\sfluxCoeff}{ O{} O{} }{\underline{F}^{#1}_{#2}}
\NewDocumentCommand{\ssource}{ O{} O{} }{S^{#1}_{#2}}
\NewDocumentCommand{\ssourceCoeff}{ O{} O{} }{\underline{S}^{#1}_{#2}}
All quantities can be expanded in the space-time basis.
For example, the expansion of space-time predictor can be written as
\begin{equation}
  \label{eq:cell-approx-space-time}
  \stpredictor[\cell] (\bm{x}, t) = \stpredictorCoeff[\cell][v,l,n] \stbasis[\cell][v,l,n](\bm{x}, t).
\end{equation}
We denote the space-time flux as $\stflux$ and the space-time source as $\stsource$ with coefficient vectors $\stfluxCoeff$ and $\stsourceCoeff$.
This is a part where we notice the computational advantage of the nodal approach:
The coefficients correspond to the quantity evaluated at the basis node!

Inserting \cref{eq:cell-approx-space-time} results in a local systems of equations that can be by a fixed point iteration scheme.
To show the computational efficiency of our scheme, we follow the approach of~\cite{dumbser2008unified} and collect our integrals into matrices\todo{Source is Dominics \aderdg-document.}.
Henceforth, we drop the cell index for all quantities.
For the space-time predictor, we introduce an iteration counter $i$.
To close the iterative scheme, we set the initial value for the space-time predictor as
\begin{equation}
  \label{eq:initial-guess}
 \stpredictorCoeff[i](t=0) = \ssolCoeff[i]
\end{equation}
which corresponds to a stationary guess\todo{This is an expansion only in space!}.
\newcommand{\pleft}{\bm{L}}
\newcommand{\prightsol}{\bm{r}}
\newcommand{\prightpred}{\bm{w}}
We arrive at the matrices
\begin{equation}
  \label{eq:matrices}
  \pleft \in \mathbb{R}^{\NVar \stbasisSize \times \NVar \stbasisSize}, \quad
  \prightsol \in \mathbb{R}^{\NVar \stbasisSize}, \quad
  \prightpred \in \mathbb{R}^{\NVar \stbasisSize}
\end{equation}
with entries
\begin{align}
  \label{eq:predictor-matrices}
\begin{split}
  \pleft_{(n v l), (n' v l')} &=
\intdcell{
  \sttestfunction[][v,l,n](\nextTime) \  \stbasis[][v,l', n'](\nextTime)
}
\\&-
\intdt{\intdcell{
  \left( \pdv{}{t} \sttestfunction[][v,l,n] (t) \right) \stbasis[][v,l',n'] (t)
}}
\end{split}
\\
\begin{split}
\prightsol_{v, l,n} (\stpredictor) =&
\intdcell{
  \sttestfunction[][v,l,n] (t) \sbasis[][v,n'] \ssolCoeff[][v,n']
}
\\&+
\intdt{\intdcell{
  \sttestfunction[][v,l,n] (t) \stbasis[][v,l',n'](t) S_{v,l',n'}(\stpredictor[i])
}}                             
\end{split}
  \\
\prightpred_{v,l,n} (\stpredictor) &=
\stfluxCoeff[][v,l',n'] (\stpredictor)
\intdt{\intdcell{
  \left( \gradient{\sttestfunction[][v,l,n]} \right) \stbasis[][v,l',n'](t)
}}
\end{align}
Note here that $\prightpred$ is constant during a interation step.
Using these matrices, we can solve for the space-time-predictor with the iterative scheme
\begin{align}
  \label{eq:predictor-iterative}
  \pleft \stpredictorCoeff[i+1] &= \prightsol (\dsol) - \prightpred(\stpredictorCoeff[i]) \\
 \stpredictorCoeff[i+1] &= \pleft^{-1} \left( \prightsol (\dsol) - \prightpred(\stpredictorCoeff[i]) \right).
\end{align}
For details and proof of convergence for the linear case, see~\cite{dumbser2008unified}.

@@

\sidetitle{Corrector}
The final step of the \aderdg{}-scheme is the corrector.
For this step, we write the approximation of a function $q$ in a cell as
\begin{equation}
  \label{eq:cell-approx-space}
  q(\bm{x})_{|\cell[i]} = \hat{u}^n_{i,l} \sbasis{l}(\bm{x}),
\end{equation}
where the basis, unlike in \cref{eq:cell-approx-space-time}, does not depend on the time.
We then multiply the system \cref{eq:conservation-law-gradient} by a test function $\stestfunction{i}$ and integrate over the space-time volume $(\cell \times [t^n, t^{n+1}])$.
We arrive yet again at the weak formulation of the \pde\
\begin{equation}
  \label{eq:weak-pde}
\intdt{\intdcell{
\stestfunction{k} \pdv{\Q}{t}
}}
+
\intdt{\intdcell{
    \stestfunction{k} \left( \div{F(\Q, \gradQ } \right)
}}
=
\intdt{\intdcell{
    \stestfunction{k} S(\Q, \bm{x}, t)
}}.
\end{equation}
\todo{Include gradient everywhere!}
\todo{Double check the following description}
We now replace the solution $\bm{Q}$ with the spacetime-predictor $\stpredictor (\bm{x},t)$ and write it as a polynomial using the representation of \cref{eq:cell-approx-space,eq:cell-approx-space-time}\todo{Not all quantities are defined over time}.
Integrate first by parts in time (note basis here not defined over time), flux divergence by parts in space.
\newcommand{\massMatrixDef}{\intdcell{
  \stestfunction[][n] \sbasis[][n']
}}
\todo{Fix following equation, sum only needed due to expansion of dsol}
\begin{align}
\begin{split}
\label{eq:corrector}
\sum_{n' = 0}{\stbasisSize}
\left(
\massMatrixDef
\right)
(\bm{u^{n+1} - u^{n}})
&+
\left(\intdt{\intdcellb{
      \stestfunction[][n] \Riemann(\stpredictor[-], \stpredictor[+]) \cdot \normal
}}\right)
-\\
\left(\intdt{\intdcell{
    \gradient{\stestfunction[k]} \cdot  \flux(\spredictor, \gradient{\spredictor}) % todo correct gradient?
}}\right)
&=
\left(\intdt{\intdcell{
      \stestfunction[k] \source(\spredictor)
}}\right)
\end{split}
\end{align}
The first term is our mass matrix with entries
\newcommand{\massMatrix}[1][]{\bm{M}_{#1}}
\begin{equation}
  \label{eq:mass-matrix}
  \massMatrix[kl] = \massMatrixDef = \volume \underbrace{\quadWeight[k] \delta_{kl}}_{\text{diagonal}}
\end{equation}
which is, due to the orthogonal basis \pcref{eq:basis-orthogonality}, diagonal and thus trivial to invert.
\newcommand{\basisSize}{(N+1)^d - 1}
\newcommand{\sumbasis}{\sum_i^{\basisSize}}
We can then insert the definition of our basis function into our equation and arrive at
\begin{align}
  \massMatrix \left( \ssolCoeff[t+1] - \ssolCoeff[t] \right) &=
  \Delta t \left( \bm{a} - \bm{b} + \bm{s} \right) 
  \intertext{with}
\begin{split}
a_{v,n} &= \sfluxCoeff[][n'] \intdcell{
  \sbasis[][v,n'] \gradient{\sbasis[][v,n]}(t)
}
\\
b &= \ldots \\
s_n &=
\ssourceCoeff[][v,n'] \intdcell{
  \sbasis[][v,n] \sbasis[][v,n']
}
,
\end{split}
\end{align}
where we evaluated the time-integrals by using the fact that our quantities are time-averaged.
We can solve this for the new unknows $\bm{u}^{n+1}$
\begin{align}\label{eq:update-predictor}
\begin{split}
  \bm{u}^{n+1} &= \bm{u}^{n} + \Delta t (\operatorname{update}) \\
  \operatorname{update} &= \massMatrix^{-1} \left( \bm{a} - \bm{b} + \bm{s} \right)
\end{split}
\end{align}
which is clearly of the form of a one-step scheme.

@@

\section{Adaptive Mesh Refinement \textit{\&} Finite Volume Limiting}\label{sec:grid}
\todo{Grid, spacefilling curve, and so on.}
This section is concerned with two different but related concepts:%
adaptive mesh refinement \amr{} and finite volume limiting.
Both have in common that they change the structure of the grid.
Instead of a regular grid where each cell has the same size, we now have different cell sizes.

\subsection{Adaptive Mesh Refinement}\label{sec:amr}
The goal of \amr{} is increasing the computational efficiency by using a higher spatial resolution in areas of interest.
A simple example for this would be using finer mesh cells for the simulation of a wave, while using a low resolution for areas where the wave does not pass through.
Of course, the difficult part is defining areas of interest.
We use a global, gradient based refinement strategy.
We first describe the computation of our indicator variable and then describe a simple way how one can detect outliers.

>>>>

% Stuff for numerics
\newcommand{\domain}{\Omega}
\newcommand{\broken}{\domain}
\newcommand{\cell}[1][]{C_{#1}}
\newcommand{\boundary}{\partial \domain}
\newcommand{\lagrange}[1][i]{\varphi_{#1}}
\newcommand{\lagrangeRef}[1][i]{\hat{\varphi}_{#1}}
\NewDocumentCommand{\sbasis}{ O{} O{} }{\phi^{#1}_{#2}}
\NewDocumentCommand{\stbasis}{ O{} O{} }{ \Theta^{#1}_{#2}}
\NewDocumentCommand{\sbasisRef}{ O{} O{} }{\hat{\phi}^{#1}_{#2}} %{\hat{\sbasis[#1][#2]}}
\NewDocumentCommand{\stbasisRef}{ O{} O{} }{\hat{\Theta}^{#1}_{#2}} %{\hat{\stbasis[#1][#2]}}
%\newcommand{\stestfunction}[1]{\sbasis[#1]}
\NewDocumentCommand{\stestfunction}{ O{} O{} }{\sbasis[#1][#2]}
\NewDocumentCommand{\sttestfunction}{ O{} O{} }{\stbasis[#1][#2]}
\newcommand{\normal}{\bm{n}}
\newcommand{\dsol}[1][h]{\bm{u}_{#1}}

% Space-time dofs
\NewDocumentCommand{\stpredictor}{ O{} O{} }{\overline{\bm{q}}^{#1}_{#2}}
\NewDocumentCommand{\stpredictorCoeff}{ O{} O{} }{\underline{\overline{q}}^{#1}_{#2}}

\NewDocumentCommand{\stflux}{ O{} O{} }{\overline{F}^{#1}_{#2}}
\NewDocumentCommand{\stfluxCoeff}{ O{} O{} }{\underline{\overline{F}}^{#1}_{#2}}

\NewDocumentCommand{\stsource}{ O{} O{} }{\overline{S}^{#1}_{#2}}
\NewDocumentCommand{\stsourceCoeff}{ O{} O{} }{\underline{\overline{S}}^{#1}_{#2}}

\NewDocumentCommand{\ssol}{ O{} O{} }{u^{#1}_{#2}}
\NewDocumentCommand{\ssolCoeff}{ O{} O{} }{\underline{u}^{#1}_{#2}}

\NewDocumentCommand{\sflux}{ O{} O{} }{F^{#1}_{#2}}
\NewDocumentCommand{\sfluxCoeff}{ O{} O{} }{\underline{F}^{#1}_{#2}}

% Space dofs
\NewDocumentCommand{\spredictor}{ O{} O{} }{\bm{q}^{#1}_{#2}}
\NewDocumentCommand{\spredictorCoeff}{ O{} O{} }{\underline{q}^{#1}_{#2}}

\NewDocumentCommand{\ssource}{ O{} O{} }{S^{#1}_{#2}}
\NewDocumentCommand{\ssourceCoeff}{ O{} O{} }{\underline{S}^{#1}_{#2}}

@@

The Jacobian determinant of $\mapping$ is simply the volume $V$ of the cell
\begin{equation}
  \label{eq:determinant-mapping}
  \volume = \operatorname{det}(\operatorname{Jacobian}\mapping) = \Delta x \, \Delta y \,\Delta z,
\end{equation}
the Jacobian determinant of $\timeMapping$ is $\Delta t$.
This is useful for evaluating derivatives by the chain rule and, similarly, integrals by substitution.
For example, we can evaluate a volume integral by
\begin{equation}
  \label{eq:integration-by-substitution}
  \intdcell{
f(\bm{x})
  }
  =
\volume \intdrefcell{
    \hat{f}(\hat{\bm{x}})
  }
\end{equation}
\sidetitle{Basis Functions}
The next step is the definition of basis functions for the reference cell.
We use Langrange polynomials that are defined in the one-dimensional case for the reference interval $(0,1)$ by
\begin{align}
  \label{eq:lagrange-basis}
    \lagrangeRef(x) = \prod_{i \neq n}^N \frac{x - {\quadNode{j}}}{x_i - \quadNode[j]},
\end{align}
We can then approximate functions as a sum over the support points $\quadNode[j]$
\begin{equation}
  \label{eq:langrange-expansion-1d}
  f(x) = \sum_{i = 0}^N f(x_i) \lagrangeRef[i](x) = f(x_i) \lagrangeRef[i](x),
\end{equation}
where we used the Einstein summation convention where summation over repeated indices is implied\todo{Remove this sentence, or sentence before introducing einstein summation!}.
The support points $\quadNode[n]$ are chosen such that they coincide with the nodes of the Gauss-Legendre quadrature of order $N+1$ which we can use to evaluate integrals
\begin{equation}
  \label{eq:quadrature-1d}
  \int_0^1 f(x) \dd{x} = \sum_n^{N+1} \quadWeight[n] f(x_n),
\end{equation}
where $\quadNode[n]$ is a quadrature point with corresponding weight $\quadWeight[n]$.

The basis functions are similarly defined in $\dimensions$-dimensions by considering nodes that are the tensor-products of $d$ one-dimensional Gauss-Legendre quadrature.
To simplify notation, we order the polynomials
\begin{equation}
  \label{eq:basis-space}
  \sbasisRef[][n] (\bm{x}) = \prod_{i=0}^{\dimensions} \lagrangeRef[n] (x_i)
\end{equation}
by a linearised index, a $d$-dimensional function is then approximated by
\begin{equation}
  \label{eq:lagrange-expansion}
  f(\bm{x}) = \sum_{i = 0}^{\sbasisSize} f(\bm{x}_i) \lagrangeRef[i](\bm{x}) = f(\bm{x}_i) \lagrangeRef[i](\bm{x}).
\end{equation}
Similarly to the one-dimensional case, we can evaluate integrals by
\begin{align}
  \label{eq:quadrature}
  \underbrace{\int_0^1 \cdots \int_0^1}_{\dimensions \text{ times}} f(\bm{x}) \dd{\bm{x}} &= \sum_n^{\sbasisSize} \quadWeight[n] f(\quadNode[n]) \\
  \intertext{with}
  \quadWeight[n] &= \prod_{i}^{d} \quadWeight[i].
\end{align}
\todo{Fix notation, especially multi-dimensional integral.}
% TODO: Quadrature

Two important properties of this family of polynomials are
  \begin{alignat}{10}
    \label{eq:basis-interpolating}
&& \text{Interpolating:} \qquad && \lagrangeRef[i] (\quadNode[i]) &= \delta_{ij}\\
\label{eq:basis-orthogonality}
&& \text{Orthogonality:} \qquad &&
\underbrace{\int_0^1 \cdots \int_0^1}_{d \,\text{times}}
\lagrangeRef[i] \left( \hat{\bm{x}} \right)
\lagrangeRef[j] \left( \hat{\bm{x}} \right) \dd{\hat{\bm{x}}}
&= \quadWeight[i] \delta_{ij}
    \end{alignat}
\todo{Fix this for multiple integrals!}

We define the basis functions over a space-cell with an index $n = 0, \ldots, \sbasisSize$
\begin{align}\label{eq:space-basis}
  \begin{split}
  \sbasis[][n] (\bm{x}) &= \sbasisRef[][n] \left( \mapping(\bm{x}) \right)
  \end{split}
\end{align}
where $\sbasisRef$ denotes the basis function on the reference cell.
Similarly, we define a basis for a space-time reference element defined over $(0, 1)^D \times (0, 1)$
\begin{align}\label{eq:space-time-basis}
  \begin{split}
  \stbasisRef[][l,n](\hat{\bm{x}}, \hat{t}) &= \lagrange[l](t) \sbasis[][n] (x) = \lagrange[l](t) \lagrange[n](x)\\
  \stbasis[][l,n] (\bm{x}, t) &= \stbasisRef \left( \mapping(\bm{x}), \timeMapping(t) \right)
  \end{split}
\end{align}
where the first index $l = 0, \ldots, N$ runs over times.
Outside of elements, we define the basis functions to be equal to 0.

We introduce an additional index $v = (0, \ldots, \NVar - 1)$ that corresponds to a variable.
The complete basis functions are then defined by
\begin{align}
  \stbasis[][v,l,n] (\bm{x},t)= \bm{I} \otimes \stbasis[][l,n] (\bm{x}, t)
\end{align}
with the identity matrix $\bm{I} \in \mathbb{R}^{\NVar}$\todo{Write out definition for space-time basis+both reference basis funcs}.

@@

We integrate the first term by parts in time and the flux divergence in space.
Here we do not use the Riemann solver for the flux boundary term but rather use the discrete solution at time $t$\todo{Insert in equation!}.
This corresponds to upwinding in time~\cite{dumbser2008unified}.
Note that this neglects the interaction with neighbouring cells.
We account for this in the corrector step.
\begin{align}\label{eq:space-time-predictor}
\begin{split}
\intdcell{
  \sttestfunction[\cell][k] (\bm{x}, t^{n+1}) \stpredictor(\bm{x}, t^{n+1})
}
&-
\intdt{\intdcell{
    \pdv{}{t} \sttestfunction[\cell][k] (\bm{x}, t) \stpredictor(\bm{x}, t)
}}
= \\
\intdcell{
  \sttestfunction[\cell][k] (\bm{x},t^n) \stpredictor(\bm{x}, t^n)
}
&+
\intdt{\intdcell{
    \sttestfunction[\cell][k] (\bm{x},t) \divergence{\flux(\stpredictor, \gradient{\stpredictor})}
}}
+
\intdt{\intdcell{
    \sttestfunction[\cell][k] (\bm{x}, t) \source(\stpredictor)
}}
\end{split}
\end{align}
All quantities can be expanded in the space-time basis.
For example, the expansion of space-time predictor can be written as
\begin{equation}
  \label{eq:cell-approx-space-time}
  \stpredictor[\cell] (\bm{x}, t) = \stpredictorCoeff[\cell][v,l,n] \stbasis[\cell][v,l,n](\bm{x}, t).
\end{equation}
We denote the space-time flux as $\stflux$ and the space-time source as $\stsource$ with coefficient vectors $\stfluxCoeff$ and $\stsourceCoeff$.
This is a part where we notice the computational advantage of the nodal approach:
The coefficients correspond to the quantity evaluated at the basis node!
Similarly, we define the space degrees of freedoms by an expansion in the space basis, for example for the space-predictor
\begin{equation}
  \label{eq:cell-approx-space}
  \spredictor[\cell] (\bm{x}) = \spredictorCoeff[\cell][v,n] \sbasis[\cell][v,n] (\bm{x}),
\end{equation}
where the basis, unlike in \cref{eq:cell-approx-space-time}, does not depend on the time\todo{Maybe move to averaging in time?}.

Inserting \cref{eq:cell-approx-space-time} results in a local systems of equations that can be by a fixed point iteration scheme.
To show the computational efficiency of our scheme, we follow the approach of~\cite{dumbser2008unified} and collect our integrals into matrices\todo{Source is Dominics \aderdg-document.}.
Henceforth, we drop the cell index for all quantities.
For the space-time predictor, we introduce an iteration counter $i$.
To close the iterative scheme, we set the initial value for the space-time predictor as
\begin{equation}
  \label{eq:initial-guess}
\forall l: \quad \stpredictorCoeff[i][v,l,n] = \ssolCoeff[v,n]
\end{equation}
which corresponds to a stationary guess\todo{This is an expansion only in space!}.
\newcommand{\pleft}{\bm{L}}
\newcommand{\prightsol}{\bm{r}}
\newcommand{\prightpred}{\bm{w}}
We arrive at the matrices
\begin{equation}
  \label{eq:matrices}
  \pleft \in \mathbb{R}^{\NVar \stbasisSize \times \NVar \stbasisSize}, \quad
  \prightsol \in \mathbb{R}^{\NVar \stbasisSize}, \quad
  \prightpred \in \mathbb{R}^{\NVar \stbasisSize}
\end{equation}
with entries
\begin{align}
  \label{eq:predictor-matrices}
\begin{split}
  \pleft_{(n v l), (n' v l')} &=
\intdcell{
  \sttestfunction[][v,l,n](\nextTime) \  \stbasis[][v,l', n'](\nextTime)
}
\\&-
\intdt{\intdcell{
  \left( \pdv{}{t} \sttestfunction[][v,l,n] (t) \right) \stbasis[][v,l',n'] (t)
}}
\end{split}
\\
\begin{split}
\prightsol_{v, l,n} (\ssol) =&
\intdcell{
  \sttestfunction[][v,l,n] (t) \sbasis[][v,n'] \ssolCoeff[][v,n']
}
\\&+
\intdt{\intdcell{
  \sttestfunction[][v,l,n] (t) \stbasis[][v,l',n'](t) S_{v,l',n'}(\stpredictor[i])
}}                             
\end{split}
  \\
\prightpred_{v,l,n} (\stpredictor) &=
\stfluxCoeff[][v,l',n'] (\stpredictor)
\intdt{\intdcell{
  \left( \gradient{\sttestfunction[][v,l,n]} \right) \stbasis[][v,l',n'](t)
}}
\end{align}
Note here that $\prightpred$ is constant during a interation step.
Using these matrices, we can solve for the space-time-predictor with the iterative scheme
\begin{align}
  \label{eq:predictor-iterative}
  \pleft \stpredictorCoeff[i+1] &= \prightsol (\ssol) - \prightpred(\stpredictorCoeff[i]) \\
 \stpredictorCoeff[i+1] &= \pleft^{-1} \left( \prightsol (\ssol) - \prightpred(\stpredictorCoeff[i]) \right).
\end{align}
For details and proof of convergence for case of linear \pde{}s, see~\cite{dumbser2008unified}.

@@

\sidetitle{Corrector}
The final step of the \aderdg{}-scheme is the corrector.
We then multiply the system \cref{eq:conservation-law-gradient} by a test function $\stestfunction{i}$ and integrate over the space-time volume $(\cell \times [t^n, t^{n+1}])$.
We arrive yet again at the weak formulation of the \pde\
\begin{equation}
  \label{eq:weak-pde}
\intdt{\intdcell{
\stestfunction[][v,n] \pdv{\Q}{t}
}}
+
\intdt{\intdcell{
    \stestfunction[][v,n] \left( \div{F(\Q, \gradQ } \right)
}}
=
\intdt{\intdcell{
    \stestfunction[][v,n] S(\Q, \bm{x}, t)
}}.
\end{equation}
\todo{Include gradient everywhere!}
\todo{Double check the following description}
We now replace the solution $\bm{Q}$ with the spacetime-predictor $\stpredictor (\bm{x},t)$ and write it as a polynomial using the representation of \cref{eq:cell-approx-space,eq:cell-approx-space-time}\todo{Not all quantities are defined over time}.
The first part can be integrated by parts in time with the convenient result that only the boundary terms remain because the basis is constant in time.
We then integrate the flux divergence by parts in space and insert the Riemann solver to connect with the neighbouring elements.
Finally, we need to solve
\newcommand{\massMatrixDef}{\intdcell{
  \stestfunction[][v,n] \sbasis[][v,n']
}}
\todo{Fix following equation, sum only needed due to expansion of dsol}
\begin{align}
\begin{split}
\label{eq:corrector}
% \sum_{n' = 0}^{\stbasisSize}
\left(
\massMatrixDef
\right)
(\ssolCoeff[t^{n+1}][v,n'] - \ssolCoeff[t^n][v,n'])
&+
\left(\intdt{\intdcellb{
      \stestfunction[][v,n] \Riemann(\spredictor[-], \spredictor[+]) \cdot \normal
}}\right)
-\\
\left(\intdt{\intdcell{
    \gradient{\stestfunction[v,n][k]} \cdot  \flux(\spredictor, \gradient{\spredictor}) % todo correct gradient?
}}\right)
&=
\left(\intdt{\intdcell{
      \stestfunction[v,n][k] \source(\spredictor)
}}\right)
\end{split}
\end{align}
for the coefficients $\ssolCoeff[\nextTime][v,n]$ of the new solution.
Here $\spredictor[\pm]$ are the boundary extrapolated space-predictors.
Again, the computational effort can be vastly reduced, by collecting the integrals in matrices and precomputing as much as possible.
The first term is thed mass matrix with entries
\newcommand{\massMatrix}[1][]{\bm{M}_{#1}}
\begin{equation}
  \label{eq:mass-matrix}
  \massMatrix[n n'] = \massMatrixDef = \volume \underbrace{\quadWeight[n] \delta_{n n'}}_{\text{diagonal}}
\end{equation}
which is, due to the orthogonal basis \pcref{eq:basis-orthogonality}, diagonal and thus trivial to invert.
\newcommand{\basisSize}{(N+1)^d - 1}
\newcommand{\sumbasis}{\sum_i^{\basisSize}}
We can then insert the definition of our basis function into our equation and arrive at
\begin{align}
  \massMatrix \left( \ssolCoeff[t+1] - \ssolCoeff[t] \right) &=
  \Delta t \left( \bm{a} - \bm{b} + \bm{s} \right) 
  \intertext{with}
a_{v,n} &= \sfluxCoeff[][n'] \intdcell{
  \sbasis[][v,n'] \gradient{\sbasis[][v,n]}(t)
}
\\
\label{eq:corrector-surface}
b_{v,n} &= \intdcellb{
    \stestfunction[][v,n] \Riemann(\spredictor[-], \spredictor[+]) \cdot \normal
} \\
s_n &=
\ssourceCoeff[][v,n'] \intdcell{
  \sbasis[][v,n] \sbasis[][v,n']
}
,
\end{align}
where we evaluated the time-integrals by using the fact that our quantities are time-averaged.
The surface integral \pcref{eq:corrector-surface} can be evaluated by summing over the contributions of the faces of each cell, which are computed by integrating the extrapolated space predictor with Gaussian quadrature.
We can solve \cref{eq:corrector} for the new unknows $\bm{u}^{n+1}$
\begin{align}\label{eq:update-predictor}
\begin{split}
  \bm{u}^{n+1} &= \bm{u}^{n} + \Delta t (\operatorname{update}) \\
  \operatorname{update} &= \massMatrix^{-1} \left( \bm{a} - \bm{b} + \bm{s} \right)
\end{split}
\end{align}
which is clearly of the form of a one-step scheme.

@@

\section{Adaptive Mesh Refinement \textit{\&} Finite Volume Limiting}\label{sec:grid}
\todo{Grid, spacefilling curve, and so on.}
This section is concerned with two different but related concepts:%
finite volume limiting and adaptive mesh refinement (\amr{}).
Both have in common that they change the structure of the grid.
Instead of a regular grid where each cell has the same size, we now have different cell sizes.
